%!TEX root = /lecture/Discrete_Optimistic.tex

\section{Flow Network}
\subsection{Definition}
\newcommand{\val}{\mathrm{val}}
\begin{example}
    For directed graph  $ G=(V,E,s,t,c) $ where  $ s  $ is the source and  $ t  $ is the sink. $ c:E\rightarrow \Rbb_{ \geq 0}  $ is the capacity function.
    
    The \name{st-flow} is   $ f:E\rightarrow \Rbb_{ \geq 0} $ \st 
    \begin{enumerate}[label=\arabic*)]
        \item  $ \forall e\in E $, $ f(e) \leq c(e) $.
        \item  $ \forall v\in V\setminus\{s,t\} $,  $ \dps\sum_{(u,v)\in E}f(u,v)=\sum_{(v,u)\in E}f(v,u) $, \ie flow conservation.
    \end{enumerate} 
    \[\val(f)=\sum_{(s,u)\in E}f(s,u)-\sum_{(u,s)\in E}f(u,s)\]
    Our goal is to maximize  $ \val(f) $ 
\end{example}
An \textbf{st-cut} is a partition  $ (A,B) $ of  $ V $ such that  $ s\in A,t\in B $, the capacity 
\[c(A,B)=\sum_{\substack{(u,v)\in E\\u\in A,v\in B}}c(u,v)\]   
\begin{claim}
    $ \forall  $ feasible flow  $ f $ and st-cut  $ (A,B) $, 
    \[\val(f) \leq c(A,B)\]  
\end{claim}
\paragraph{Residual Network} Given flow network  $ G $, feasible flow  $ f $, the residual network $ G_f(v,E_f,s,t,c_f) $ is for each  $ e\in E $ 
\[c_f(e)=c(e)-f(e)+f(e^{\mathrm{reverse}})\]
where  $ u\to v $ is on the flow.
\begin{claim}[Weak Duality]
    $ f' $ is a feasible flow in  $ G_f $ if and only if  $ f\oplus f' $ is feasible in  $ G $, where 
    \[(f\oplus f')(e)=f(e)+f'(e)-f'(e^{\mathrm{reverse}})\]    
\end{claim}     

An \textbf{augmenting path}  $ P $ is an unsaturated  $ s\to t $ path in  $ G_f $.

\begin{algorithm}
    \caption{Augment $ (f,P) $}
    \begin{algorithmic}[1]
        \STATE Let  $ \delta=\dps\min_{e\in P}c_f(e) $.
        \FOR{$ e=(u,v)\in P $}
            \IF{ $ e\in E $ }\STATE$ f(e)\leftarrow f(e)+\delta $
            \ELSE \STATE $ f(v,u)\leftarrow f(v,u)-\delta $
            \ENDIF
        \ENDFOR
    \end{algorithmic}
\end{algorithm}


Now we give the Ford-Fulkerson Algorithm.
\begin{algorithm}
    \caption{Ford-Fulkerson Algorithm}
    \begin{algorithmic}[1]
        \STATE $ f\leftarrow 0 $
        \WHILE{ $ \exists $ augmenting path $ P $ in  $ G_f $}
            \STATE Augment$ (f,P) $
        \ENDWHILE
        \RETURN $ f $
    \end{algorithmic}
\end{algorithm}
\begin{theorem}\label{max flow algorithm thm}
    If F-F algorithm terminates, it finds a max flow.
\end{theorem}

\begin{claim}
    $ \forall $ st-cut  $ (A,B) $, st-flow  $ f $, we have 
    \[\val(f)=\sum_{\substack{u\in A,v\in B\\(u,v)\in E}}f(u,v)-\sum_{\substack{u\in E,v\in A\\(u,v)\in E}}f(u,v)\]   
\end{claim}
It proves the previous claim weak duality.
\begin{proof}
    \begin{align*}
        \val(f)&=\sum_{(s,v)\in E}f(s,v)-\sum_{(u,s)\in E}f(u,s)\\
        &+\sum_{\omega\in A-\{s\}}\left(\sum_{(u,w)\in W}f(u,w)-\sum_{(w,v)\in E}f(w,v)\right)
    \end{align*}
\end{proof}
\begin{proof}[Proof of the Theorem \ref{max flow algorithm thm}]
    Consider the residue graph  $ G $.
    
    Denote  $ A $ to be the set of nodes reachable from  $ s $.
    $ B=V\setminus A $.  $ t\in B $ since there is no path from  $ s $ to  $ t $.   
    
    Then st-cut  $ (A,B) $ has capacity  $ c_f(A,B)=0 $. So for  $ u\in B,v\in A $, since  $ f(u,v)\neq 0 $  $ \Rightarrow  $ $ c_f(v,u)>0 $, we have  $ c_f(v,u)=0 $    $ \Rightarrow  $ $ f(u,v)=0 $.   
    
    \begin{align*}
        \val(f)&=\sum_{\substack{u\in A,v\in B\\(u,v)\in E}}f(u,v)-\sum_{\substack{u\in B,v\in A\\(u,v)\in E}}f(u,v)\\
        &=\sum_{\substack{u\in A,v\in B\\(u,v)\in E}}c(u,v)-0\\
        &=c(A,B)
    \end{align*}
\end{proof}

Now suffices to proof that the algorithm terminates.

\begin{lemma}
    If capacities are integral and less than  $ c $, then F-F terminates in  $ O(nmC) $ time and returns an integral max flow.  
\end{lemma}

The lemma implies we should choose some proper path so that it will terminate fast.

Assume the integral capacities  $  \leq C $ and  $ G_f(\Delta) $ denoted as  $ G_f $ with edges of capacites  $  \geq \Delta $.    
\begin{algorithm}
    \caption{Capacity-Scaling Algotihm}
    \begin{algorithmic}[1]
        \STATE Initiate  $ f\equiv 0 $,  $ \Delta\leftarrow  $ largest  $ 2^k \leq c $.  
        \WHILE{$ \Delta \geq 1 $}\label{CS algorithm loop}
            \WHILE{ $ \exists $ augmenting path $ P $ in  $ G_f(\Delta) $}
                \STATE Augment$ (f,P) $
            \ENDWHILE
            \STATE $ \Delta\leftarrow \Delta/2 $ 
        \ENDWHILE
    \end{algorithmic}
\end{algorithm}

\begin{theorem}
    The C-S runs in time  $ O(m^2\log c) $ since the step \ref{CS algorithm loop} runs for  $ O(m) $ iterations. 
\end{theorem}
